%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[colorlinks = true, linkcolor = RoyalBlue, urlcolor  = RoyalBlue, citecolor = RoyalBlue, anchorcolor = RoyalBlue]{hyperref}
\name{Louis CUNY} % Your name
\address{\href{mailto:louiscuny@gmail.com}{louiscuny@gmail.com}~$\cdot$~github: \href{http://github.com/lou}{@lou}~$\cdot$~+33(0)615446404} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{\href{http://octoly.com}{Octoly}}{Jully 2013 - Present}{Web Developer}{NYC, USA}
\item I'm currently in charge of the public API from authentication to performance through documentation.
\item Working with Rails 4, Elasticsearch, DynamoDB, MySQL.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{\href{http://letitcast.com}{Letitcast}}{Mars 2009 - June 2013}{Web Developer}{Paris, France}
\item Took charge of the service on both frontend and backend with Rails, Sinatra and jQuery.
\item Built a Sinatra service to handle ftp uploads and encoding.
\item Migrated the monolithic application to a backend API + 4 frontends and used rails engines to share code and assets between clients.
\item Helped maintaining the applications from rails 2.3.10 to rails 3.2.8.
\item Frequent use of various APIs: Amazon S3 and CloudFront, Zencoder, Scribd, Embedly, Postmark, HipChat.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{\href{http://eyeka.com}{Eyeka}}{January 2008 - January 2009}{Intern~$\cdot$~Web Developer}{Paris, France}
\item I worked on parts of the back and front office.
\item Built a contacts importer compatible with Gmail, Hotmail, Yahoo and Facebook.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{\href{http://capocea.com}{Capocea}}{May - October 2007}{Intern~$\cdot$~Web Developer}{Paris, France}
\item I took charge of a bunch of websites for photographer, sailmaker and realtors.
\item I worked on the second version of the backoffice.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{\href{http://nadeo.com}{Nadeo}}{May - September 2005}{Intern~$\cdot$~Game Developer}{Paris, France}
\item Participation in the development of Virtual Skypper 4 and TrackMania Nation.
\item I created an internal designer tool to create in-game clouds which is still in use for all Nadeo's games.
\item I worked with C++ and 3DSMax.
\end{rSubsection}


\end{rSection}
%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{\href{http://epitech.com}{EPITECH} - European Institute of Technology}{2004 - 2009}{Bachelor degree in Computer Science}{Paris, France}
\item
\end{rSubsection}
\begin{rSubsection}{\href{http://www.isquareit.ac.in/}{I2IT}, International Institute of Information Technology}{2004 - 2009}{Master in Computer Engineering (discontinued)}{Pune, India}
\item
\end{rSubsection}


\end{rSection}
%----------------------------------------------------------------------------------------
% Skills SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\textbf{Open-source:}
I'm the author and maintainer of 3 jQuery plugins: \href{http://loudev.com}{multiselect}, \href{https://github.com/lou/switchy}{switchy}, \href{https://github.com/lou/listy}{listy}.
I'm also making my debut as a Javascript game developer with \href{http://lou.github.io/seagull/}{my seagull buddy} !\\

\textbf{Natural languages:}
French (mother tongue), English (professional proﬁciency)

\end{rSection}

%----------------------------------------------------------------------------------------
% EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Interests}

Sailing, windsurfing, climbing, guitar, coding, traveling\ldots

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
